Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-08 paper/main.tex
[issue 2.13] restructure sentence

The input to a convolutional layer is an image with a certain number of color channels
or \textit{feature maps}.
To produce output feature maps, we convolve each feature map with a set of weights
called \textit{filters},
and apply a non-linearity such as ReLU to the weighted sum of these convolutions.
Different feature maps use different sets of filters,
but all neurons in a feature map share the same set of filters.
Mathematically, we replace the dot product in Equation~\ref{eq:neuron_output}
with a sum of convolutions. Thus, the $k$-th feature map is given by
\begin{equation}
  y^k = \sigma \left( \sum_{m} \bmath{w}_m^k \ast \bmath{x}_m + b^k \right),
\end{equation}
where we sum over the set of input feature maps,
$\ast$ is the convolution operator, and $\bmath{w}_m^k$ represent the filters.

>>>>

\added{
The input to a convolutional layer is an image, and the output channels of
each layer are called \textit{feature maps}.
}
To produce output feature maps, we convolve each feature map with a set of weights
called \textit{filters},
and apply a non-linearity such as ReLU to the weighted sum of these convolutions.
Different feature maps use different sets of filters,
but all neurons in a feature map share the same set of filters.
Mathematically, we replace the dot product in Equation~\ref{eq:neuron_output}
with a sum of convolutions. Thus, the $k$-th feature map is given by
\begin{equation}
  y^k = \sigma \left( \sum_{m} \bmath{w}_m^k \ast \bmath{x}_m + b^k \right),
\end{equation}
where we sum over the set of input feature maps,
$\ast$ is the convolution operator, and $\bmath{w}_m^k$ represent the filters.
